The problem and promise of scale in multilayer networks

### 2019-09-11 paper/unstructured.Rmd
rm temporal

## Skeleton
* Abstract
* Brief introduction
  * Networks, social networks, animal social systems 
  * Landscape ecology, scale
* Multilayer Networks
  * What is a ML network
  * What kinds of ML nets exist
  * Which are relevant to spatial variables
* Scale 
  * What is scale
  * In LE lit, how has scale been investigated
  * Elements of scale relevant to animal social systems, animal movement data, landcover data
* Box 1: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
* Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data
* Simulations
* Discussion/results
* Brief conclusion

>>>>

## Skeleton
* Abstract
* Brief introduction
  * Networks, social networks, animal social systems 
  * Landscape ecology, scale
* Multilayer Networks
  * What is a ML network
  * What kinds of ML nets exist
  * Which are relevant to spatial variables
* Scale 
  * What is scale
  * In LE lit, how has scale been investigated
  * Elements of scale relevant to animal social systems, animal movement data, landcover data
* Box 1: Types of spatially explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
* Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data
* Simulations
* Discussion/results
* Brief conclusion
